### 2023-11-08 manuscript/supplementary_tables.Rmd
Correctly format the adducts in table S2

mzAnnotation::adduct_rules() %>% 
  dplyr::filter(Name %in% adducts) %>% 
  dplyr::select(
    Adduct = Name,
    Charge,
    `No. molecules` = xM,
    `Mass difference` = Add
  ) %>% 
  mutate(`Mass difference` = round(`Mass difference`,5)) %>% 
  knitr::kable(caption = 'Information for positive and negative mode adducts used for calculating ionisation products.',
               format = 'latex',
               booktabs = TRUE)
```

>>>>

mzAnnotation::adduct_rules() %>% 
  dplyr::filter(Name %in% adducts) %>% 
  dplyr::select(
    Adduct = Name,
    Charge,
    `No. molecules` = xM,
    `Mass difference` = Add
  ) %>%
  mutate(
    Adduct = Adduct %>% 
      stringr::str_replace_all(']1-',']$^{1-}$') %>% 
      stringr::str_replace_all(']2-',']$^{2-}$') %>% 
      stringr::str_replace_all('Cl37','$^{37}$Cl') %>% 
      stringr::str_replace_all(stringr::coll(']1+'),']$^{1+}$') %>% 
      stringr::str_replace_all(stringr::coll(']2+'),']$^{2+}$') %>% 
      stringr::str_replace_all('K41','$^{41}$K'),
    `Mass difference` = round(`Mass difference`,5)
    ) %>% 
  knitr::kable(caption = 'Information for positive and negative mode adducts used for calculating ionisation products.',
               format = 'latex',
               escape = FALSE,
               booktabs = TRUE)
```
